---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(lobstr)
```
# lobstr

[![Travis-CI Build Status](https://travis-ci.org/r-lib/lobstr.svg?branch=master)](https://travis-ci.org/r-lib/lobstr)
[![Coverage status](https://codecov.io/gh/r-lib/lobstr/branch/master/graph/badge.svg)](https://codecov.io/github/r-lib/lobstr?branch=master)

lobstr provides tool in the same vein as `str()`, tools that allow you to dig into the detail of an object.

## Installation

You can install the development version with:

``` r
# install.packages("devtools")
devtools::install_github("r-lib/lobstr")
```
## Example

`ast()` draws the abstract syntax tree of R expressions:

```{r example}
ast(a + b + c)

ast(function(x = 1) {
  if (x > 0) print("Hi!")
})
```

`ref()` shows hows objects can be shared across data structures by digging into the underlying __ref__erences:

```{r}
x <- 1:1e6
y <- list(x, x, x)
ref(y)

e <- rlang::env()
e$self <- e
ref(e)
```

A related tool is `obj_size()`, which computes the size of an object taking these shared references into account:

```{r}
obj_size(x)
obj_size(y)
```

